---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

[![Lifecycle: deprecated](https://img.shields.io/badge/lifecycle-deprecated-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#deprecated)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# mcmcrdata

## Introduction

`mcmcrdata` is an R package to manipulate Monte Carlo Markov Chain samples and data.

## Installation

To install the latest version from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/mcmcrdata")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "mcmcrdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/mcmcrdata/issues).

[Pull requests](https://github.com/poissonconsulting/mcmcrdata/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## Inspiration

- coda and rjags
